Two applications of logic programming to Coq

### 2020-11-07 papers/types2020/cultures.tex

Another difference between \lP and functional programming can be
illustrated by considering how they are used in the specification of
tactics.  The origin story for the ML functional programming language
was that it was the meta-language for implementing the LCF suite of
tactics and tacticals \cite{gordon79}.  To implement tactics, ML
adopted not only novel features such as polymorphically typed
higher-order functional programming but also the non-functional
mechanisms of failure and exception handling.  While \lP is also based
on ML-style-polymorphically typed higher-order relational
programming\footnote{It uses types to indicate syntactic categories, while
  any dependency information needs to be captured using predicates and
  logical connectives and quantifiers.}, it also comes with a
completely declarative version of failure and backtracking search.
Combining those features along with its support of unification (even
in the presence of term-level bindings), \lP provides a rather
different approach to the specification of tactics \cite{felty93jar}.

@@

% LocalWords:  Elpi polymorphically

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

Another difference between \lP and functional programming can be
illustrated by considering how they are used in the specification of
tactics.  The origin story for the ML functional programming language
was that it was the meta-language for implementing the LCF suite of
tactics and tacticals \cite{gordon79}.  To implement tactics, ML
adopted not only novel features such as polymorphically typed
higher-order functional programming but also the non-functional
mechanisms of failure and exception handling.  While \lP is also based
on ML-style polymorphically typed higher-order relational
programming\footnote{It uses types to indicate syntactic categories, while
  any dependency information needs to be captured using predicates,
  logical connectives, and quantifiers.}, it also comes with a
completely declarative version of failure and backtracking search.
Combining those features along with its support of unification (even
in the presence of term-level bindings), \lP provides a rather
different approach to the specification of tactics \cite{felty93jar}.

@@

% LocalWords:  Elpi polymorphically Gentzen disjunction Herbrand HOAS

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
% LocalWords:  coinductive Abella LCF tacticals
